### 2022-05-10 README.Rmd
update README with roadmap (#18)
add some minimal instructions for setting up hipergator access (closes #20)

@@

>>>>

# Roadmap

Before June 3:

-   [x] Finish building all IPMs
-   [x] Document functions and \_targets.R
-   [ ] Calculate bootstrapped 95% CIs around all lambdas
-   [ ] Finish writing methods section
-   [ ] Draft tables & figures
-   [ ] Archive draft of code in Zenodo

Future:

-   [ ] Finish writing and revising
-   [ ] Submit

@@

### NOTES:

-   The targets `lambda_bt_dlnm_ff` and `lambda_bt_dlnm_cf` will take a very long time to run (days), so you may want to comment those out before attempting to reproduce results.
-   If you want to make use of HPC, follow instructions [here](https://github.com/BrunaLab/hipergator-targets-ssh) to customize templates and options.
